\documentclass[fleqn,reqno]{amsart}
\usepackage{../lib/radoslav-macro}
\usepackage{../lib/radoslav-more}
\usepackage{times}
\usepackage{natbib}

\begin{document}
%% STRIP END



\begin{paragraf*}
The goal of this chapter is to set up the notation and recall some basic facts
which we shall need later on.
The first section defines the main objects of interest and establishes some
standard notation and terminology.
Section 2 is a short and elementary treatment on strands of maps of free modules
in the way we shall need them.
Section 3 is solely devoted to the notion of multiplicity.
It comes in many flavors and some care is needed when dealing with it.
\end{paragraf*}

\begin{paragraf*}
Section~\ref{sec:def-examples}, we present two examples with the sole purpose
of working out the definitions of the previous three sections.
\end{paragraf*}



\section{Notation}
\label{sec:notation}

\begin{paragraf}
\label{par:cox-ring}
Let $X$ be a non-degenerate toric variety of dimension $n-1$.
We shall not entertain our readers in defining what a toric variety is,
but rather point them to \citet{CLSh11}.

Throughout the thesis,
we work exclusively with the Cox ring $S$ of $X$, \citet{Cox-93}.
Let $\Delta$ be the fan of $X$ and
$\Delta(1)=\{\rho_1,\ldots,\rho_m\}\se\Delta$ be the set of 1-dimensional cones.
We take
\[
	S=\CC[s_1,\ldots,s_m]
\]
with the grading induce by
\[
	0\To\ZZ^{n-1}\cong\mathbf M\To\ZZ^m\To\Pic(X)\To0
\]
A monomial $\mathbf s^\alpha$ corresponds to the divisor $\sum_k \alpha_k[\rho_k]$.
While this suffice to define the grading on $S$,
we need to define an analogue to the irrelevant ideal for $\PP^n$,
in order to recover $X$.
We define
\[
	\n=\la \prod_{\rho_k^\perp}s_k\not\in\sigma~:~\sigma\in\Delta\ra
\]
\end{paragraf}

\begin{paragraf}
From now on we use the notation $\Proj(S,\mathfrak n)$ for the construction of a projective toric variety from
its Cox ring. In the cases where the irrelevant ideal $\mathfrak n$ is the usual one,
for example for products of projective spaces, or is not relevant to the discussion,
we shall simply write $\Proj(S)$.
This is within reason because the construction coincides with the usual construction
in case $S$ is standardly graded.
\end{paragraf}

\begin{paragraf}
\label{par:setup}
Let $X$ be a smooth projective toric variety of dimension $n-1$ ($n>1$).
Let $S$ be its Cox ring \eqref{par:cox-ring} and
let $S'$ be any homogeneous coordinate ring
furnishing an embedding of $X$ into projective space, i.e. $X=\Proj(S')$ with
\[
	S'=\CC[s_0,\ldots,s_m]/\mathfrak{p}
\]
for some homogeneous prime $\mathfrak{p}$ of height $m-n+1$.
Let $T=\CC[\mathbf x]$ be the homogeneous coordinate ring of $\PP^n$.

Let $\L$ be a line bundle on $X$ such that $h^0(\L)> n$.
Because $X$ is toric,
there is a degree $\mathbf e$ on $S$ such that $\L\cong\O_X(\mathbf e)$.

Under the identification above, suppose that
\[
\phi_0,\ldots,\phi_n\in H^0(X,\L)=S_{\mathbf e}
\]
are linearly independent and consider the rational map
\[
	\phi=(\phi_0,\ldots,\phi_n):X\To\PP^n=\Proj(T)
\]

We denote by $J$ the ideal of the coordinates $\phi_j$,
\[
	J=\la\phi_0,\ldots,\phi_n\ra\se S
\]

We assume from now on that the closed image of $\phi$, which we denote by $Y$,
is of dimension $n-1$.
Since $X$ is reduced and irreducible, so is $Y$ and, in particular,
$Y=V(P)$ for some principal homogeneous prime ideal $P\se T$,
\[
	Y=\image(\phi)=V(P)
\]

If we want to refer to a generator of $P$, necessarily up to a unit in $T$,
we shall dereference the ideal by writing $P(\mathbf x)$.

We sometimes refer to $S$ as the ring of \underbar{s}ource and
to $T$ as the ring of the \underbar{t}arget.
\end{paragraf}

\begin{paragraf}
Throughout this thesis, the term {\em image of a rational map}, as used in \eqref{par:setup},
means the scheme-theoretic image, also called the closed image. Formally,
\[
	Y = V(\ker\phi^\#),\quad \phi^\#:\O_{\PP^n}\To\phi_\ast\O_X
\]
In our situation, this is just the closure of the set-theoretic map on closed points.
\end{paragraf}

\begin{paragraf}
\label{par:blowup-algebras}
Let $R=S\tensor T=S[\mathbf x]$. Then $R$ is naturally bigraded by
\[
	\deg(af)=(\mathbf d,i)
\]
whenever $a\in S_{\mathbf d}\se R$ and $f\in T_i\se R$.
Let $S[t]$ be similarly graded, setting $\deg(t)=(-\mathbf e,1)$.
The blow-up algebras, $\Rees_S(J)$ and $\Sym_S(J)$, naturally become
factor rings of $R$ as follows.

The Rees algebra is the image of the bigraded map of $S$-algebras
\[
	\beta:R\To S[t]:\quad x_j\mapsto\phi_j\cdot t
\]

The Rees ideal of $J$ is the bigraded ideal $I=\ker(\beta)\se R$.
It is generated by the the polynomial relations on the generators $\phi_0,\ldots,\phi_n$ of $J$,
that is,
\[
	I=\la \textstyle\sum_{|\alpha|=i} a(\mathbf s){\mathbf x}^{\alpha}
	~\boldsymbol:~
	\textstyle\sum_{|\alpha|=i} a(\mathbf s){\mathbf \phi}^{\alpha}=0
	~\boldsymbol;~\forall i\ra\se R
\]
For the sake of brevity, we denote the Rees algebra by $B$.

While $\Rees_S(J)$ captures all polynomial relations on the $\phi_j$,
the symmetric algebra $\Sym_S(J)$ captures only the linear ones.
Specifically, we have
\[
	\Sym_S(J)=R/\la \textstyle\sum_j a(\mathbf s)x_j
	~\boldsymbol:~
	\textstyle\sum_j a(\mathbf s)\phi_j=0
	\ra
\]

We shall sometimes refer to $R$ as the ambient ring of the blow-up algebras.
\end{paragraf}

\begin{paragraf}
\label{par:the-graph}
The ring $R=S[\mathbf x]$ and the blow-up algebras just defined are in essence geometric objects.
As $\CC$-algebras, $R$ corresponds to the bihomogeneous coordinate ring of the product of
the source and the target varieties,
and $B=\Rees_S(J)$ --- to the coordinate ring of the graph of $\phi$, $\Gamma(\phi)$,
defined (e.g. \citet{Har92}) as the closure of
\[
	\{(q,\phi(q)):q\in X\}\se X\times \PP^n
\]

The natural surjective morphisms $R\To \Sym_S(J)\To \Rees_S(J)$ induce natural closed embeddings
\begin{align}
\label{eq:R-Sym-B}
\Gamma(\phi)=\Biproj(\Rees_S(J))\To \Biproj(\Sym_S(J))\To \Biproj(R)=X\times \PP^n
\end{align}
\end{paragraf}

\begin{paragraf}
\label{par:base-locus}
Denote the subscheme $V(J)\se X$ by $Z$.
Then $Z$ is the base locus of the rational map.
Geometrically, $\Biproj(B)$ is the blow-up of the variety $X$ along the closed $Z$.
See Lemma~\ref{lemma:lengthRees} for details.
\end{paragraf}

\begin{paragraf}
\label{par:ci-points}
Let $X$ be a variety and $q\in X$ be a smooth point, that is,
such that the stalk $\O_q$ is regular local.
Let $Z\se X$ be a closed subscheme containing the point $q$.
We say that $q$ is a complete intersection (c.i.) point of $Z$
if the stalk of $q$ on $Z$, $\O_{q,Z}$,
is a complete intersection factor ring of the regular local $\O_q$.
Now suppose $Z\se X$ is of codimension $d$ at $q$
and that the stalk $O_{q,Z}$ can be defined from $\O_q$ by $d+1$ elements.
In this case, we say that $q$ is an almost complete intersection (a.c.i.)
point of $Z$.
\end{paragraf}

\begin{paragraf}
\label{par:linear-type}
Suppose that the base locus of the rational map $\phi$, $V(J)$, is zero-dimensional.
The first embedding in \eqref{eq:R-Sym-B} is an isomorphism if and only if
$V(J)$ is a locally complete intersection scheme.
For a proof in our setting, see (\citet{BJ-03}, Proposition 4.14).

Loosely speaking, this follows because either condition is equivalent to $J$ being of linear type.
For future reference, this does not mean that $N=N_1$.
\end{paragraf}

\begin{paragraf}
\label{lemma:push-gens}
The ideal $I$ is bigraded in $R$, so its $S$-graded pieces are finite $T$-modules.
We denote the graded piece in degree $\d$ on $S$ by $I_{\d,\bullet}$,
and sometimes call it a ($T$-)strand of $I$.

More generally, let $\mathbf M$ be a finite bigraded $R$-module
generated by some finite set $\{h_\ell:\ell\}$.
Let $\d$ be any degree on $S$.
Setting $({\mathbf a}_\ell,i_\ell)=\deg(h_\ell)$, one has
\[
	\displaystyle\sum_{\ell,~{\mathbf b}_\ell~:~{\mathbf a}_\ell+{\mathbf b}_\ell=\d}
	(R_{{\mathbf b}_\ell,\bullet}) h_\ell={\mathbf M}_{\d,\bullet}
\]
so
\[
	\displaystyle\bigcup_{\ell}~\{\mathbf s_k\cdot h_\ell:\Span_\CC\{\mathbf s_k:k\}=
	S_{{\mathbf b}_\ell}\}
\]
is finite and a $T$-module generating set for $\mathbf M_\d$.
\end{paragraf}

\begin{paragraf}
\label{par:moving-planes-notation}
For a fixed degree $\mathbf d$ on the source,
the elements of $I_{\mathbf d,i}$ are degree-$i$ syzygies of the $\phi_j$ with (module-)coefficients
in $S_{\mathbf d}$.
For specific degrees $\mathbf d$ and $i=1,2$, these have been called moving planes and quadrics,
respectively [references].
We shall only use this notation in Chapter \ref{ch:koszul-bpf} when we present a sort of a "template proof"
and use prove two results relating our work to what is already known in the case of
basepoint-free maps over $\PPP$ and $\PP^2$,
as well as a couple of new results along those lines.
\end{paragraf}

\begin{paragraf}
\label{par:basis}
Throughout this thesis we work with a fixed monomial order on $S$ (or rather $S'$).
For example, this could be the graded lexicographic order but the specific choice
is immaterial. With this convention, the statement
\begin{itemize}
\item[]
\text{let $\mathbf b$ be a row-vector corresponding to the basis of $S_{\mathbf d}$}
\end{itemize}
would mean a row vector having having as its coordinates the monomials of $S$,
listed in the selected order.

In this sense, and fixing some basis on $T$ too, we shall write
\[
\mt{basis}(S_{\mathbf d}),\quad\mt{basis}(T_i),\quad\mt{basis}(R_{\mathbf d,i})
\]
for the row vectors consisting of monomial bases in the chosen order for the $\CC$-vector spaces
$S_{\mathbf d}, T_i$  and $R_{\mathbf d,i}$, respectively.
\end{paragraf}

\begin{paragraf}
\label{par:syzygies}
Let $r=\dim_\CC(S_{\mathbf d})$ and
let $\mathbf b=\mt{basis}(S_{\mathbf d})$ be the row-$r$-vector of the monomial basis of $S$ in degree $\mathbf d$.
We shall mostly use $r$ instead of $\dim_\CC(S_{\mathbf d})$ when $\mathbf d$ has been fixed.

Given a form $g(\mathbf x)=g(\mathbf s;\mathbf x)\in I_{\mathbf d,i}$,
that is, a syzygy of degree $i$ over $S_{\mathbf d}$,
we can write $g(\mathbf x)$ as
\[
g(\mathbf x)=\mathbf b\cdot C=
\begin{bmatrix}
	x_0^i& x_0^{i-1}x_1& \ldots& x_n^i
\end{bmatrix}\cdot C'
\]
where $C$ is an $r\times1$ column vector with entries in $T_i$,
and $C'$ is a $\binom{n+i}{n}\times1$ column vector with entries in $S_{\mathbf d}$.

We shall use the term syzygy both for the column vector $C$ and the form $g$ in the
Rees ideal.
\end{paragraf}

\begin{paragraf}
\label{par:N-matrix}
We now come to the most important bit of notation.
Let us fix a degree $\mathbf d$ on the source.
As already apperent from \eqref{par:syzygies},
identifying the generators of $I_{\mathbf d}$ with column-$r$-vectors,
$I_{\mathbf d}$ becomes a sub-$T$-module of the free graded $T^r$.

Let $N$ be the matrix built from those column-generators.
Setting $\mu=\mu(I_{\mathbf d,\bullet})$ to be the number of columns,
$N$ becomes an $r\times\mu$-matrix over $T$
and more importantly, a graded $T$-linear map
\[
N:\bigoplus_{k} T(-i_k)\To T^r
\]
whose image is just $I_{\mathbf d,i}$.

By grouping the columns corresponding to the same degree $i$ into submatrices $N_i$,
for each valid $i$ we get a single matrix whose columns are the degree $i$-syzygies over $S_{\mathbf d}$.
Clearly, $N_i$ is empty for any $i$ larger than the maximum degree $\delta$ of a minimal generator
of $I_{\mathbf d,\bullet}$.
By the assumption on the linear independence of the $\phi_j$, $N_0$ is empty too.
In any case, the $N_i$ fit together to give $N$,
\[
	N=(N_1~|~N_2~|~\ldots~|~N_\delta)
\]

In Chapter 7 we describe the close connection of $N_1$ and $N_2$ to the matrices used in
the moving planes and quadrics results.

Finally, whenever useful, we write $h_i$ for $\dim_\CC \Span (N_i)=\dim_\CC(I_{\mathbf d,i})$
and $h$ for the tuple $(h_1,\ldots,h_\delta)$.
\end{paragraf}

\begin{paragraf}
Recall that for any ideal $Q$ in a unique factorization domain $T$,
$\gcd(Q)$ is defined to be the unique minimal principal ideal which contains $Q$,
and this definition obviously generalizes the definition on elements
when $T$ is a Euclidean domain.
\end{paragraf}

\begin{paragraf}
As a final bit of notation, we mention that we use $\rad(-)$ for the radial,
and $\sat(-)$ for the saturation with respect to the irrelevant ideal.
\end{paragraf}



\section{Strands of Module Maps}
\label{sec:strands}

\begin{paragraf}
\label{par:all-phi-k}
Let us consider the coordinates of $\phi$ as a row vector over $S$. We get a graded $S$-linear map
\[
\begin{bmatrix}
	\phi_0& \phi_1& \ldots& \phi_n
\end{bmatrix}:S^{n+1}\To S^1(\e)
\]
where $S(\e)$ has the usual meaning of putting $1\in S$ in degree $-\e$.
Similarly, we can consider the graded $S$-linear map given by the quadratic monomials
of the coordinates,
\[
\begin{bmatrix}
	\phi_0^2& \phi_0\phi_1& \ldots& \phi_n^2
\end{bmatrix}:S^{(n+2)(n+1)/2}\To S^1(2\mathbf e)
\]

These two maps have a central role in the methods of moving planes and quadrics.
However, there is no reason to stop at degree $2$,
so next we describe the general situation.
\end{paragraf}

\begin{paragraf}
\label{par:strands}
Let $k$ be a positive integer and $\mathbf d$ be a fixed degree on $S$ such that $S_\d\neq0$.
Define $\phi^{(k)}$ to be the graded $S$-linear map formed by the coordinates of $\phi$,
\[
\phi^{(k)}=\begin{bmatrix}\phi_0^k& \phi_0^{k-1}\phi_1& \cdots& \phi_n^k\end{bmatrix}:
S^{\binom{n+k}{n}}\To S^1(k\mathbf e)
\]
and set $\Phi^{(k)}$ be the strand of $\phi^{(k)}$ in degree $\d$, that is,
\[
\Phi^{(k)}:S_{\mathbf d}^{\binom{n+k}{n}}\To S_{k\mathbf e+\mathbf d}^1
\]
is a map of complex vector spaces.

Choosing bases \eqref{par:syzygies}, we can think of $\Phi^{(k)}$ as a matrix over $\CC$ of size
\[
\dim_\CC(S_{k\mathbf e+\mathbf d})\times r\binom{n+k}{n}
\]
whose columns can be indexed by the monomials in $R_{\mathbf d,k}$.
\end{paragraf}

\begin{paragraf}
\label{par:syzygies-kernel}
The advantage of the matrices $\Phi^{(k)}$ over the matrices $\phi^{(k)}$
is that the kernel of $\Phi^{(i)}$ corresponds directly to the degree-$i$ syzygies over $S_{\mathbf d}$.
That is, for a fixed $\mathbf d$,
\[
\mathbf v\mapsto\mt{basis}(R_{\mathbf d,i})\cdot \mathbf v:\ker(\Phi^{(i)})\To I_{\mathbf d, i}
\]
is an isomorphism of vector spaces.
\end{paragraf}



\section{Multiplicity}
\label{sec:mult}

\begin{paragraf}
\label{par:mult-ha}
Recall the following notation from \cite{Har77}.
For a homogeneous prime ideal $P$ in a graded ring $T$,
we set $T_{(P)}$ to be the degree-$0$ graded piece of the localization of $T$
at the homogeneous elements outside of $P$.
If $P$ is a minimal prime of a graded $T$-module $\mathbf M$,
we denote by $\mult_P(\mathbf M)$ the length of the $T_P$-module $\mathbf M_P$
(see {\em loc. cit.}, I, Proposition 7.4).
\end{paragraf}

\begin{paragraf}
\label{par:mult}
Let $Z$ be a zero-dimensional closed subscheme of a smooth projective variety $X$.
Let $\mathscr{J}\se\mathscr{O}_X$ be the ideal sheaf of $Z$
and let $q\in Z$ be any point.
Since $Z$ is zero-dimensional,
$\mathscr{J}_q\se\mathscr{O}_{q,X}$ is an ideal of definition
in the regular local ring $\mathscr{O}_{q,X}$.

Define the multiplicity of $Z$ at $q$, denoted $e_q$,
to be the Hilbert-Samuel multiplicity of $\mathscr{J}_q$,
denoted $e(\mathscr{J}_q,\O_q)$ (see \citet{Eis95} or \citet{BH98}).

Define the degree of $Z$ at $q$, denoted $d_q$, to be the length of the local ring,
\[	
	\length(\mathscr{O}_{q,Z})=\dim_{\CC}(\mathscr{O}_{q,Z})
\]

We have that $d_q\leq e_q$ with equality if and only if $q$ is a c.i. point
(\citet{BH98}, Theorem 4.7.4).
\end{paragraf}

\begin{paragraf}
We shall mostly be interested in the degree and multiplicity of points on the base locus $Z$.
Since by assumption $X$ is toric, the ideal sheaf $\mathscr{J}$ of $Z$ in \eqref{par:mult}
is the ideal sheaf $\widetilde J$.
We stick to this notation for the rest of the paper.
\end{paragraf}

\begin{paragraf}
Let $\L$ be a line bundle on $X$.
We denote by $[\L]$ the class of $\L$ in the Chow ring.
Since $\dim(X)=n-1$, we can identify $[\L]^{n-1}$ with an integer --- its degree.
Suppose that the base locus $Z$ is zero-dimensional.
Then by (\citet{Ful84}, Proposition 4.4), see \citet{Cox-01} for details,
we have the formula
\begin{align}
	\label{eq:degree-formula}
	\deg(\phi)\deg(Y)=[\mathscr L]^{n-1}-\sum_{q\in Z}e(\widetilde{J}_q,\O_q)
\end{align}
\end{paragraf}

\begin{paragraf}
\label{par:self-intersection}
The self-intersection $[\mathscr L]^{n-1}$ is obvious when $X=\PP^{n-1}$.
Then $\mathscr L=\O(d)$ for some integer $d$, and
\[
	[\O(d)]^{n-1}=d^{n-1}
\]
Similarly, let $X=(\PP^1)^{n-1}$. Then $\L=\O(e_1,\ldots,e_{n-1})$ for integers $e_k$,
and
\begin{align}
	\label{eq:formula-prod-P1}
	[\O(e_1,\ldots,e_{n-1})]^{n-1}=(n-1)!\cdot e_1\cdots e_{n-1}
\end{align}
The formula above can be easily proved by remembering that the rulings of $X$ have
self-intersection zero,
so the only nonzero term in the power of $[\L]$ in the Chow ring, is the multiplication
of all rulings.
\end{paragraf}

\begin{example}
Here is a list of ways to compute the degree and multiplicity, and also
to show how not to compute them.
\begin{itemize}
	\item Both notions are geometric which means that we need to saturate our ideals
	before computing the degree and multiplicity.
	\item For both, the sum of the values at the points in a zero-dimensional scheme
	add to the corresponding notion for the scheme.
	This works better with degree.
	\item Just typing $\mt{degree}(J)$ and $\mt{multiplicity}(J)$ in Macaulay2 often
	has dissasterous results.
	\item If $X=\PP^n$ and $J$ is saturated, then $\mt{degree}(J)$ is in fact the degree
	of the zero-dimensional scheme.
	If the scheme is supported on a single point, then that's the degree of the point.
	Else, saturate with respect to the prime ideals of the other points.
	\item We can freely work over non-algebraically closed fields.
	Points in the same Galois closure are algebraically indistinguishable,
	so just assume they split equally to closed points over $\CC$, or the algebraic closure.
	\item $\mt{multiplicity}(J)$ does work in projective space for an ideal supported
	on a single point.
	And the implementation uses a cool trick --- the reference I have is due to Eisenbud.
\end{itemize}
\end{example}



\section{Examples}
\label{sec:def-examples}

\begin{example}[$\mt{ex201}$]
\label{ex201}
Let $X=\PP^1_{s,u}\times\PP^1_{t,v}$ be the product of two projective lines,
and let $S=\CC[s,u;t,v]$ be its Cox ring --- a bihomogeneous ring graded by $\Pic(X)$
such that $\deg(s)=\deg(u)=(1,0)$ and $\deg(t)=\deg(v)=(0,1)$.
The irrelevant ideal $\n$ is the product of the irrelevant ideals of the components,
\[
	\n=\la s,u\ra\cap\la t,v\ra=\la st,sv,ut,uv\ra
\]
We write $X=\Proj(S,\n)$ or simply $X=\Proj(S)$ for the construction in the toric setting.

Consider the rational map $\phi:X\To\PP^3$ given by
\[
	\phi=(s^{2} v^{2},s u v^{2},u^{2} t^{2}+u^{2} t v,s u t v-101 u^{2}t v)
\]
In this case, the coordinates $\phi_0,\ldots,\phi_3$ are global sections
of the line bundle $\O_X(2,2)$, and are linearly independent over the base field $\CC$.
Note that
\[
	h^0(\O_X(2,2),X)=\dim_\CC(S_{(2,2)})=9
\]

The ideal of the coordinates,
\[
	J=\la s^{2} v^{2},s u v^{2},u^{2} t^{2}+u^{2} t v,s u t v-101 u^{2}t v\ra\se S
\]
defines the base locus, $Z=V(J)$.
In this case, $Z$ is supported on the points
\[
	q_1=(0,1)\times(0,1) \text{ and } q_2=(1,0)\times(1,0)
\]
so the base locus is zero-dimensional and the map is generically finite.

The points are qualitatively different.
Near $q_1$ the scheme $Z$ looks like $V(s,t)$ in $\AA^2_{s,t}$,
while near $q_2$, $Z$ looks like $V(u^2,uv,v^2)$ in $\AA^2_{u,v}$.
This allows us to compute their degrees and multiplicities.
Let $\O_{q_i,Z}$ denote the stalk at $q_i$ on $Z\se X$ ($i=1,2$),
and let $\widetilde J$ denote the ideal sheaf arising form $J$.
The the degrees are
\[
	d_{q_1}=\length(\O_{q_1,Z})=1 \text{ and } d_{q_2}=\length(\O_{q_2,Z})=3
\]
while the multiplicities are
\[
	e_{q_1}=e(\widetilde{J}_{q_1},\O_{q_1,X})=1 \text{ and } e_{q_2}=e(\widetilde{J}_{q_2},\O_{q_2,X})=4
\]
where $e(\mathbf I,\mathbf R)$,
for a Noetherian local $\mathbf R$ and an ideal of definition $\mathbf I$,
denotes the Hilbert-Samuel multiplicity.

Note further that $d_{q_1}=e_{q_1}$ reflects the fact that $q_1$ is a complete intersection
(c.i.) point,
while $d_{q_2}<e_{q_2}$ so $q_2$ is not.
It is, however, an almost complete intersection (a.c.i.) point,
since it is of codimension-$2$ and is (stalk-, affine-)locally defined by $3$ equations.

The closed image $Y\se\PP^3$ of $\phi$ is given by a single equation,
\[
	P(\mathbf x)={x}_{0}^{2} {x}_{2}-202 {x}_{0} {x}_{1} {x}_{2}+10201
  {x}_{1}^{2} {x}_{2}-{x}_{0} {x}_{1} {x}_{3}+101 {x}_{1}^{2} {x}_{3}-{x}_{0}
  {x}_{3}^{2}
\]
The equation $P(\mathbf x)$, called the implicit equation, show up in the Rees ideal.

Let $B=\Rees_S(J)$ be realized as the quotient ring of $R=S[\mathbf x]$
by the aforementioned Rees ideal $I$.
In our case,
\[
	I=\Bigg\la
	\begin{cases}
	u {x}_{0}-s {x}_{1},
	(s v-101 u v) {x}_{2}+(-u t-u v){x}_{3},\\
	(t^{2}+t v) {x}_{1}-101 v^{2} {x}_{2}+(-t v-v^{2}) {x}_{3},\\
	(s t-101 ut) {x}_{1}-s v {x}_{3},v {x}_{0} {x}_{2}-101 v {x}_{1} {x}_{2}+(-t-v) {x}_{1}{x}_{3},\\
  	t {x}_{0} {x}_{2}-101 t {x}_{1} {x}_{2}-101 v {x}_{2} {x}_{3}+(-t-v){x}_{3}^{2},\\
  	s {x}_{0} {x}_{2}+(-202 s+10201 u) {x}_{1} {x}_{2}+(-s+101 u){x}_{1} {x}_{3}-s {x}_{3}^{2},\\
	t {x}_{0} {x}_{1}-101 t {x}_{1}^{2}-v {x}_{0}{x}_{3},\\P(x_0,x_1,x_2,x_3)
	\end{cases}\Bigg\ra
\]
and $P(\mathbf x)$ can be seen as the unique linear generator in bidegree $((0,0),3)$.
In fact, it is the unique $\CC[\mathbf x]$-generator of $I_{(0,0),\bullet}$.

Generalizing slightly, let $\d=(1,1)$ be a degree on $S$.
Then $I_{\d,\bullet}$ is minimally generated by 5 elements as a $\CC[\mathbf x]$-module.
Let those be $g_1(\mathbf s;\mathbf x),\ldots,g_5(\mathbf s;\mathbf x)$.
Writing
\[
	\basis(S_\d)=\begin{bmatrix}st& sv& ut& uv\end{bmatrix}
\]
to be a row vector over $R$ consisting of a linear basis for $S_\d$,
we can define the matrix $N$ over $\CC[\mathbf x]$ by the identity
\[
	\basis(S_\d)\cdot N=\begin{bmatrix}g_1&\ldots&g_5\end{bmatrix}
\]
In this case, $N$ is a $4\times5$-matrix each of whose columns contains forms of the same degree.
Specifically,
\[
	N=\begin{bmatrix}0&
	       {x}_{1}&
	       0&
	       0&
	       {x}_{0} {x}_{2}-{x}_{3}^{2}\\
	       {x}_{2}&
	       {-{x}_{3}}&
	       {-{x}_{1}}&
	       {-{x}_{3}}&
	       {-{x}_{3}^{2}}\\
	       {-{x}_{3}}&
	       {-101 {x}_{1}}&
	       0&
	       {x}_{0}-101 {x}_{1}&
	       -10201 {x}_{1} {x}_{2}-202 {x}_{3}^{2}\\
	       -101 {x}_{2}-{x}_{3}&
	       0&
	       {x}_{0}&
	       0&
	       20402 {x}_{2} {x}_{3}-202 {x}_{3}^{2}\\
	       \end{bmatrix}
\]

In this sense, $N$ is a representation matrix as well as a matrix of syzygies.
It represents a generating set for the graded syzygies of the $\phi_j$ with coefficients
in $S_{(1,1)}$.
\end{example}

\begin{example}[$\mt{ex202}$]
\label{ex202}
Let $X=\PP^2$. Its Cox ring is just its standard homogeneous coordinate ring, $\CC[s,t,u]$,
and the irrelevant ideal $\n=\la s,t,u\ra$.

Let $J\se S$ be a graded ideal generated by $4$ linearly independent forms of the same degree $\e$.
For concreteness we can take
\[
	J=\la s^3,t^2u,s^2t+u^3,stu\ra
\]
so that its generators are all $3$-forms.
We can think of $J$ as defining a rational map to $\PP^3$,
\[
	\phi=(s^3,t^2u,s^2t+u^3,stu):X\To\PP^3
\]

Then $\phi$ is a morphism on the open set away from $Z=V(J)$.
Note that $J$ is not saturated, so there is a better representative for the base locus scheme,
i.e.
\[
\sat(J)=J:\n^\infty=\la s^2,u\ra
\]
From this we know that $Z$ is supported on $q=(0,0,1)$ only,
and that $q$ is a complete intersection point, so its degree and multiplicity coincide,
\[
	\e_q=d_q=\length(\O_q/\widetilde{J}_q)=2
\]

Let $P$ be the principal ideal generated by the implicit equation for $\phi$.
By the formulas in Section~\ref{sec:mult}, we have
\[
	\deg(\phi)\deg(P)=3^2-e_q=7
\]
Since the coordinates $\phi_j$ are not linearly dependent,
and they never will be in this thesis,
$\deg(P)\neq1$, so $\deg(\phi)=1$ and the map is generically 1-1.
We then have that the implicit equation is a septic.
Indeed,
\[
	P(\mathbf x)={x}_{0}^{3} {x}_{1}^{4}-{x}_{0}^{2} {x}_{1}^{3} {x}_{2} {x}_{3}+{x}_{3}^{7}
\]

Besides a rational map, or a ring map in the form of $\phi^\#$,
$\phi$ can be made into a map of free $S$-modules.
For example, we have that
\[
	\phi^{(1)}=\begin{bmatrix}\phi_0&\ldots&\phi_3\end{bmatrix}:S^4\To S^1(3)
\]
is a graded map of $S$-modules.

We can linearize this map in this map in the following way.
Take a degree on $S$, for concreteness, take $\d=1$.
We take a the strand of the map $\phi^{(1)}$ in degree $\d=1$.
To this end, note that the basis on the LHS can be indexed by the monomials in $R_{1,1}$,
for example, by putting
\[
	\begin{bmatrix}0\\s\\0\\0\end{bmatrix}=sx_1
\]
and the basis on the RHS can be indexed by the monomials in $S_4$.
Multiplying out $\phi^{(1)}$ with an element $S^4$ is then equivalent to evaluation $x_j=\phi_j$.
Reading off the coefficients we get for the linearization
\[
	\Phi^{(1)}=
	\bgroup\makeatletter\c@MaxMatrixCols=12\makeatother\begin{bmatrix}1&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0\\
      0&
      0&
      1&
      0&
      1&
      0&
      0&
      0&
      0&
      0&
      0&
      0\\
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      1&
      0&
      0&
      0\\
      0&
      0&
      0&
      0&
      0&
      0&
      1&
      0&
      0&
      0&
      0&
      0\\
      0&
      0&
      0&
      1&
      0&
      0&
      0&
      0&
      0&
      0&
      1&
      0\\
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0\\
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0\\
      0&
      1&
      0&
      0&
      0&
      0&
      0&
      1&
      0&
      0&
      0&
      0\\
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      1\\
      0&
      0&
      1&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0\\
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0\\
      0&
      0&
      0&
      0&
      0&
      1&
      0&
      0&
      0&
      0&
      0&
      0\\
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      1&
      0&
      0\\
      0&
      0&
      0&
      0&
      0&
      0&
      1&
      0&
      0&
      0&
      0&
      0\\
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      0&
      1&
      0\\
      \end{bmatrix}\egroup
\]

We end this example noting that $\ker(\Phi^{(1)})$ is isomorphic to $I_{1,1}$.
In our situation this is easy to check.
The kernel is spanned by
\[
	\mathbf v=\bgroup\makeatletter\c@MaxMatrixCols=12\makeatother\begin{bmatrix}0&
	      {-1}&
	      0&
	      0&
	      0&
	      0&
	      0&
	      1&
	      0&
	      0&
	      0&
	      0\\
	      \end{bmatrix}\egroup\T
\]
which corresponds to $I_{1,1}=\Span_\CC(sx_1-tx_3)$
after multiplication with the indexing set for the columns,
\[
	\basis(R_{1,1})=\bgroup\makeatletter\c@MaxMatrixCols=12\makeatother\begin{bmatrix}s {x}_{0}&
      s {x}_{1}&
      s {x}_{2}&
      s {x}_{3}&
      t {x}_{0}&
      t {x}_{1}&
      t {x}_{2}&
      t {x}_{3}&
      u {x}_{0}&
      u {x}_{1}&
      u {x}_{2}&
      u {x}_{3}\\
      \end{bmatrix}\egroup
\]
\end{example}



%% STRIP BEGIN
%% BIBLIOGRAPHY
\bibliographystyle{unsrtnat}
\bibliography{../lib/refs}

\end{document}